---
title: "Risk Assessment with Custom Configurations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Risk Assessment with Custom Configurations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `assess_pkg_r_package()` function in the `risk.assessr` package allows users to evaluate the risk of an R package. You can pass a custom risk configuration to control how risk levels are interpreted.

This vignette demonstrates:

- Running the function with the default risk configuration
- Running it with two different custom configurations

## Load the Package

```{r, message=FALSE, warning=FALSE}
library(risk.assessr)
options(repos = c(CRAN = "http://cran.us.r-project.org"))
```

## Example 1: Use Default Configuration

```{r, message=FALSE, warning=FALSE}
result_default <- risk.assessr::assess_pkg_r_package("stringr")
```

```{r, message=FALSE}
str(result_default$risk_analysis)
```

## Example 2: Use Custom Configuration (Strict Code Coverage)

```{r, message=FALSE, warning=FALSE}

strict_coverage_config <- list(
  list(
    label = "code coverage",
    id = "code_coverage",
    key = "code_coverage",
    thresholds = list(
      list(level = "high", max = 0.9999),
      list(level = "low", max = NULL)
    )
  ),
  list(
    label = "popularity",
    id = "popularity",
    key = "last_month_download",
    thresholds = list(
      list(level = "high", max = 21200000),          
      list(level = "medium", max = 11200000),      
      list(level = "low", max = NULL)       
    )
  )
)

# Set the option
options(risk.assessr.risk_definition = strict_coverage_config)
result_strict <- risk.assessr::assess_pkg_r_package("stringr")

```

```{r}
str(result_strict$risk_analysis)
```

## Summary

The `risk_config` parameter allows you to tailor the risk scoring logic to your organization’s policies. You can use it to enforce stricter standards, accommodate internal tooling priorities, or meet compliance requirements.
