---
title: "risk.assessr metrics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{risk.assessr metrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(risk.assessr)
```

```{r acquisition, eval=FALSE}
here <- risk.assessr::assess_pkg_r_package("here")
```

# Package Risk Assessment Summary

This report presents a risk assessment of the R package: **here**.


## Metadata

```{r, eval=FALSE}
here$results[c("pkg_name", "pkg_version", "sysname", "release", "date_time")]
```


## Documentation Metrics

```{r, eval=FALSE}
here$results[c("license_name", "has_examples", "has_vignettes", "has_news", 
               "has_website", "has_source_control", "export_help", 
               "export_calc", "covr", "check")]
```

## Dependencies

```{r, eval=FALSE}
here$results$dependencies
```

## Test Coverage

```{r, eval=FALSE}
here$covr_list$res_cov$coverage$totalcoverage
```

## CRAN Check Results

```{r, eval=FALSE}
here$check_list$res_check$errors
```


## Popularity Metrics

### CRAN Downloads

```{r, eval=FALSE}
here$results$download
```

### GitHub Statistics

```{r, eval=FALSE}
here$results$github_data
```

### Reverse Dependencies (Extended)

```{r, eval=FALSE}
head(here$results$rev_deps, 10)  
```

## Authorship

```{r, eval=FALSE}
here$results$author
```

## Hosting Information

```{r, eval=FALSE}
here$results$host
```

## Suggested Imports Review

```{r, eval=FALSE}
here$risk_analysis
```


## Advanced feature

### Traceability Matrix

```{r, eval=FALSE}
here$tm_list
```

## Suggested Imports Review

```{r, eval=FALSE}
here$results$suggested_deps
```


